Parameter space representation of Pareto set

### 2013-09-25 introduction.tex
splitted sections

\documentclass[final,journal,letterpaper]{IEEEtran}

\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{balance}
\usepackage{float}
\usepackage{threeparttable}

\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{amsthm}

\usepackage{mathptmx}
\usepackage[scaled=.90]{helvet}
\usepackage{courier}

\usepackage{listings}
\usepackage{listings}

\lstset{
   language=C,
   basicstyle=\small,
   keywordstyle=\bfseries,
   identifierstyle=\ttfamily,
   stringstyle=\ttfamily,
   numbers=left,
   numberstyle=\tiny,
   stepnumber=1,
   numbersep=-5pt,
   showstringspaces=false
%   frame=single %trbl%
}

\usepackage[normalem]{ulem}

%------------------------------------------------------------------------------

\newcommand{\etal}{\emph{et al.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\etc}{\emph{etc.}}
\renewcommand{\baselinestretch}{0.98}\normalsize
%------------------------------------------------------------------------------
\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\theoremstyle{definition}
\newtheorem{defn}[thm]{\protect\definitionname}
\theoremstyle{remark}
\newtheorem{rem}[thm]{\protect\remarkname}

\makeatother

%\usepackage{babel}
\providecommand{\definitionname}{Definition}
\providecommand{\remarkname}{Remark}
\providecommand{\theoremname}{Theorem}

\begin{document}

\author{Vincenzo~Catania, Andrea Araldo~and~Davide~Patti% 
\thanks{The authors are with the Dipartimento di Ingegneria
Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
(email: \{vincenzo.catania,aaraldo,davide.patti\}@dieei.unict.it).}}

\title{Parameter space representation of Pareto set}
%ATTENZIONE: in questo testo io mi sono riferito a ``Pareto set''
%come un sottoinsieme dello spazio degli obiettivi (vedi, ad es., descrizione
%dell'algoritmo). E' più corretto forse, invece, intendere il Pareto
%set come un sottoinsieme dello spazio delle configurazioni.

\maketitle
\begin{abstract}
In this paper ...
\end{abstract}

%------------------------------------------------------------------------------
%\IEEEkeywords{...}

\begin{IEEEkeywords}
Nanotechnology, DNA, Self-assembly, Routing
\end{IEEEkeywords}
%------------------------------------------------------------------------------
\section{Introduction}

@@

\section{Preliminaries}

\subsection{Representation}
\begin{defn}
\emph{Configuration}

Let $p_{1},\dots,p_{n}$ be the parameters and $P_{i}$ the domain
of $p_{i}$, i.e. the set of values $v\in P_{i}$ that parameter $p_{i}$
may assume. A configuration is a vector
\[
\mathbf{p}=\left(v_{1},\dots,v_{n}\right)\in P_{1}\times\dots\times P_{n}
\]

\end{defn}

\begin{defn}
\emph{Objective function}

Let $o_{1},\dots,o_{m}$ be the objectives and $O_{i}$ the set of
values that $o_{i}$ may assume. Let $O_{i}$ have a ``better than''
operator $\vartriangleright$ defined so that, taking $o_{i},q_{i}\in O_{i}$,
we can always say:
\[
o_{i}\vartriangleright q_{i}\mbox{ (}o_{i}\mbox{ is better than }q_{i}\mbox{)}
\]
 or
\[
o_{i}\vartriangleleft q_{i}\mbox{ (}o_{i}\mbox{ is worse than }q_{i}\mbox{)}
\]
 or
\[
o_{i}\bowtie q_{i}\mbox{ (}o_{i}\mbox{ is neither better nor worse than }q_{i}\mbox{)}
\]

$o_{i}$ can be viewed as a function
\[
o_{i}:\mathbf{p}\rightarrow o_{i}\left(\mathbf{p}\right)\in O_{i},\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
\]
 To take into account all of the objectives, the following function
is defined:
\[
\mathbf{o}:\mathbf{p}\rightarrow\left(o_{1}\left(\mathbf{p}\right),\dots,o_{m}\left(\mathbf{p}\right)\right),\ \forall\mathbf{p}\in P_{1}\times\dots\times P_{n}
\]

\end{defn}

{[}BISOGNEREBBE INTRODURRE IL CONCETTO DI FEASIBILITY{]}
\begin{defn}
\emph{\label{pers02.def:Pareto-set}Pareto set}

Let $U\subseteq P_{1}\times\dots\times P_{n}$. The set of its dominated
configurations is:
\[
Dom\left(U\right)=\left\{ \left.\mathbf{p}\in U\right|\exists\mathbf{x}\in U:o_{i}\left(\mathbf{x}\right)\vartriangleright o_{i}\left(\mathbf{p}\right),\mbox{for }i=1,\dots m\right\} 
\]

Its Pareto set is defined as:
\[
\mathscr{P}\left(U\right)=U\setminus Dom\left(U\right)
\]

When there is no ambiguity, $\mathscr{P}$ is written instead of $\mathscr{P}\left(U\right)$.
\end{defn}

\begin{defn}
\emph{Pareto front}

The Pareto front is the representation in the objective space of the
Pareto set, i.e.:
\[
\mathbf{o}\left(\mathscr{P}\right)\in O_{1}\times\dots\times O_{m}
\]

\end{defn}
On the contrary, we call ``parameter space representation'' of the
Pareto set the representation in which each configuration $\mathbf{p}$
is simply represented as a point of $P_{1}\times\dots\times P_{n}$
space. We will investigate the relation between the ``objective space
representation'' and the ``parameter space representation''. We
are particularly interested in the relation between the evolution
of the objective space representation of the Pareto set and the evolution
of its parameter space representation.

!!! FORSE NON E' VERO CHE NOI WILL INVESTIGATE .... FORSE IL PERIODO
PRECEDENTE NON VA PIU' BENE PERCHE' NON TROVA RISCONTRO NEL RESTO
DELLA TRATTAZIONE

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/Pareto_set_and_front}

\caption{Relation between Pareto set (its ``parameter space representation'')
and Pareto front (``objective space representation'')}

\end{figure}

\subsection{Regions}

In the design process, there are often a lot of ``local decisions''
in which the designer can take advantage of well-known results or
heuristics. For example, in a VLIW architecture consider a configuration
with very few registers. It is well-known that, in such a condition,
increasing the number of ALUs doesn't lead to tangible better performances
but leads to an increase in area occupation. An intelligent exploration
algorithm wouldn't waste time evaluating configurations with many
ALUs and few registers. If $p_{1}$ is the parameter ``number of
registers'' and $p_{2}$ is the parameter ``number of ALUs'', we
can say that the region:
\[
R=\left\{ \left.\left(v_{1},v_{2}\right)\in P_{1}\times P_{2}\right|v_{1}<s_{1},v_{2}>s_{2}\right\} 
\]
 (where $s_{1}$ and $s_{2}$ are some threshold values) is of little
interest. This example shows that some ``dependency relation'' between
parameters may exist and can be exploited to guide the exploration:
the dependencies between parameters can suggest to the designer that,
if a parameter lies in a range, there are ranges of the other there
aren't worth exploring. Intuitively, the Cartesian product of these
ranges is an ``uninteresting region''.

The problem is that, in complex scenarios, not all relations of this
kind are known in advance. Some dependency may exist but may be hidden
to the designer. Or there may be ``local dependencies'', i.e. two
parameters may be related by a dependency but only if their values
lie on some ranges (so we can't treat them as they were related by
a true dependency). Therefore, as stated in section \ref{sec:Related-work},
setting up an exploration trying to take into account as much dependencies
as possible is a very hard task that is destined to be incompletely
accomplished. We need a methodology to ``automatically'' recognize
interesting or uninteresting regions without requiring a priori knowledge
to the designer.

We also consider, in measuring how much iteresting a region is, the
``innovation'' that it adds. If, during a design space exploration,
a Pareto front is temporarily calculated, adding a new Pareto front
point near to the previous ones is not a considerable ``innovation'',
because the way it fulfils the objectives is very similar to other
already evaluated configurations. On the contrary, adding a new Pareto
front point that is very distant from previous ones is remarkable,
because it let the experimenter realize that the objectives can be
fulfilled in a completely different way from what he already found
during exploration. So a region will be evaluated ineresting as much
as how different are its added Pareto front points from the ones already
found.
\begin{rem}
We will consider only parameters $p_{i}$ with ordering, i.e. such
that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
to say $a<b$ or $a=b$ or $a>b$.
\end{rem}
{[}TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
PARAMETRI SENZA ORDINAMENTO{]}
\begin{defn}
\emph{Parameter interval}

Let $p_{i}$ be a parameter and $a_{i},b_{i}\in P_{i},a_{i}<b_{i}$.
A $p_{i}$- interval is
\[
\left[a_{i}..b_{i}\right]=\left[a_{i},b_{i}\right]\cap P_{i}
\]
 (i.e. taking the interval $\left[a_{i},b_{i}\right]$ , $\left[a_{i}..b_{i}\right]$
is the set of values of $P_{i}$ lying in $\left[a_{i},b_{i}\right]$)
\end{defn}

\begin{defn}
\emph{\label{pers02.def:Contiguous-intervals}Contiguous intervals}

Let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
be two $p_{i}$-intervals. They are said to be contiguous iff
\begin{itemize}
\item $\left[a_{i}..b_{i}\right]\cap\left[x_{i}..y_{i}\right]=\emptyset$
and
\item $\left[a_{i}..b_{i}\right]\cup\left[x_{i}..y_{i}\right]$ is a $p_{i}$-
interval or $\left[x_{i}..y_{i}\right]\cup\left[a_{i}..b_{i}\right]$
is a $p_{i}$- interval
\end{itemize}
\end{defn}
\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/contiguous_intervals_or_not}

\caption{Examples of contiguous and not contiguous intervals}

\end{figure}

\begin{defn}
\emph{Region}

A region is a set of the following form:
\[
R=\left[a_{1}..b_{1}\right]\times\dots\times\left[a_{n}..b_{n}\right]=\prod\left[a_{i}..b_{i}\right]
\]
 (see figure \ref{pers02.fig:Examples-of-regions})

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/regions}

\caption{\label{pers02.fig:Examples-of-regions}Examples of regions}

\end{figure}
\end{defn}
\begin{rem}
We will talk later of ``big'' and ``small'' regions. The sense
of these terms is related to the cardinality of regions. A region
$R_{1}$ is said to be \emph{bigger }then $R_{2}$, if
\[
\left|R_{1}\right|>\left|R_{2}\right|
\]
 where $\left|R_{1}\right|$ and $\left|R_{2}\right|$ are the cardinalities
of $R_{1}$ and $R_{2}$. Similarly, a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
is said to be bigger then another $p_{i}$-interval $\left[c_{i}..d_{i}\right]$
if:
\[
\left|\left[a_{i}..b_{i}\right]\right|>\left|\left[c_{i}..d_{i}\right]\right|
\]

Therefore, the width of a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
is not given by the numeric value $b_{i}-a_{i}$ but it is its cardinality.
\end{rem}
We now provide some rules to split and merge regions. They will be
useful when explaining our proposed exploration algorithm.
\begin{defn}
\emph{\label{pers02.def:Splitting-a-region}Splitting a region}

If $\left[a_{i}..b_{i}\right]$ has more than one element, i.e. $\left|\left[a_{i}..b_{i}\right]\right|>1$,
it can be split in two contiguous intervals
\[
\left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right]
\]
 such that
\[
\begin{cases}
\left[a_{i}..c_{i}\right]\cap\left[d_{i}..b_{i}\right] & =\emptyset\\
\left[a_{i}..c_{i}\right]\cup\left[d_{i}..b_{i}\right] & =\left[a_{i}..b_{i}\right]\\
\left|\left[a_{i}..c_{i}\right]\right| & =\left\lceil \frac{\left|\left[a_{i}..b_{i}\right]\right|}{2}\right\rceil 
\end{cases}
\]

If $\left|\left[a_{i}..b_{i}\right]\right|=1$ instead, the interval
cannot be split.

If $\left[a_{i}..b_{i}\right]$ can be split, we define
\[
I_{i}=\left\{ \left[a_{i}..c_{i}\right],\left[d_{i},b_{i}\right]\right\} 
\]
 else
\[
I_{i}=\left\{ \left[a_{i}..b_{i}\right]\right\} 
\]

The whole region can be split in the following subregions
\[
\mathcal{R}^{R}=\left\{ \left.\prod\left[x_{i}..y_{i}\right]\right|\left[x_{i}..y_{i}\right]\in I_{i}\right\} 
\]

See figure \ref{pers02.fig:Splitting-a-region}.

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/splitting_the_region}

\caption{\label{pers02.fig:Splitting-a-region}Splitting a region}

\end{figure}

\end{defn}

\begin{defn}
\emph{Contiguous regions}

Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
be two regions. They are said to be contiguous iff
\begin{itemize}
\item a $j$ exists such that $\left[a_{i}..b_{i}\right]=\left[x_{i}..y_{i}\right]$
for all $i\neq j$ 
\item $\left[a_{j}..b_{j}\right]$ and $\left[x_{j}..y_{j}\right]$ are
contiguous intervals (see definition \ref{pers02.def:Contiguous-intervals})
\end{itemize}
\end{defn}
See figure \ref{pers02.fig:Contiguous-regions}.

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/contiguous_regions}

\caption{\label{pers02.fig:Contiguous-regions}Contiguous and not contiguous
regions}
\end{figure}

\begin{defn}
\emph{\label{pers02.def:Merging-regions}Merging regions}

Let $R_{1}$ and $R_{2}$ be two contiguous regions as the previous
ones. Because of the definition of contiguous intervals, it is possible
that $b_{j}<x_{j}$ or $y_{j}<a_{j}$. We can merge the contiguous
intervals and obtain a new interval, as the following
\[
\left[t_{j},z_{j}\right]=\begin{cases}
\left[a_{j}..y_{j}\right] & \mbox{ if }b_{j}<x_{j}\\
\left[x_{j}..b_{j}\right] & \mbox{ if }y_{j}<a_{j}
\end{cases}
\]

The region ``$R_{1}$ merged with $R_{2}$'' is defined as
\[
R=\prod_{i<j}\left[a_{i}..b_{i}\right]\times\left[t_{j}..z_{j}\right]\times\prod_{i>j}\left[a_{i}..b_{i}\right]
\]

Such an $R$ will be indicated with the following notation:
\[
R=R_{1}+R_{2}
\]
\end{defn}
\begin{rem}
$R_{1}+R_{2}$ is mathematically equivalent to $R_{1}\cup R_{2}$.
However, using $R_{1}+R_{2}$ notation, we enforce the argument that
$R_{1}$ and $R_{2}$ must be to contiuguous regions.
\end{rem}

\begin{defn}
\emph{Separation}

Let $\mathbf{o}=\left(o_{1},\dots,o_{m}\right)$ and $\mathbf{q}=\left(q_{1},\dots,q_{m}\right)$
be two points of $O_{1}\times\dots\times O_{m}$. The separation between
$\mathbf{o}$ and $\mathbf{q}$ is 
\[
s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\sum_{i=1}^{m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
\]

Notice that the separation is not a commutative operator.\end{defn}
\begin{rem}
The separation between $\mathbf{o}$ and $\mathbf{q}$ measures how
much we must vary $\mathbf{o}$ to transfrom it in $\mathbf{q}$.
The separation is a ``normalized'' measure that is independent of
the nature and the unit of measurement of the objectives
\end{rem}

\begin{defn}
\emph{Separation (alternative)}

Another definition of separation could be:
\[
s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\max_{i=1,\dots,m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
\]

\end{defn}

\section{The algorithm}

The algorithm we present is iterative. Each iteration is called \emph{era}.

Each era $era_{i}$ is characterized by 
\begin{itemize}
\item the set of regions $\mathcal{R}_{i}$ in which the parameter space
$P_{1}\times\dots\times P_{n}$ is divided
\item its Pareto set $\mathscr{P}_{i}$
\item a set $test_{i}$ of at most $K$ configurations to evaluate
\end{itemize}
$K$ is a parameter that must be set before the algorithm runs.

\paragraph{START CONDITION}
\begin{itemize}
\item $\mathcal{R}_{0}=\left\{ P_{1}\times\dots\times P_{n}\right\} $,
i.e. era $0$ has only one region that is the whole parameter space.
A random set $test_{0}$ of $K$ configurations is evaluated. The
Pareto set $\mathscr{P}_{0}=\mathscr{P}\left(test_{0}\right)$ is
calculated (see def \ref{pers02.def:Pareto-set} for the definition
of the operator $\mathscr{P}_{i}$ over a set)
\end{itemize}

\paragraph{ITERATION RULES}

For $era_{i}$ with $i>0$ the following operations must be performed.
\begin{enumerate}
\item \label{pers02.enu:K}For each region $R\in\mathcal{R}_{i}$, a set
$test_{R,i}$ of configurations is randomly chosen in%
\footnote{Therefore the chosen configurations can only be configurations of
$R$ not yet evaluated in past eras.%
} $R\setminus\bigcup_{j=0}^{i-1}test_{j}$. The number of configurations
in $test_{R,i}$ is set to%
\footnote{This means that $\frac{K}{\left|\mathcal{R}_{i}\right|}$ configurations
are to be chosen, but if not yet evaluated configurations in $R$
are less then $\frac{K}{\left|\mathcal{R}_{i}\right|}$, all of them
are chosen%
} 
\[
\min\left(\frac{K}{\left|\mathcal{R}_{i}\right|},\left|R\setminus\bigcup_{j=1}^{i-1}test_{j}\right|\right)
\]
The set 
\[
test_{i}=\bigcup_{R\in\mathcal{R}_{i}}test_{R,i}
\]
 is defined. 
\item All configurations on $test_{i}$ are simulated.
\item The Pareto set $\mathscr{P}_{i}$ for $era_{i}$ is defined as 
\[
\mathscr{P}_{i}=\mathscr{P}\left(test_{i}\cup\mathscr{P}_{i-1}\right)
\]

\item \label{pers02.enu:novelty_score_of_a_configuration}Every point $\mathbf{p}$
of%
\footnote{The innovation score is not given to those points in $test_{i}$ that
are not in the Pareto set%
} $test_{i}\cap\mathscr{P}_{i}$ is given an \emph{innovation score
}defined as:
\[
is\left(\mathbf{p}\right)=\min\left\{ \left.s\left(\mathbf{q}\rightarrow\mathbf{o}\left(\mathbf{p}\right)\right)\right|\mathbf{q}\in\mathscr{P}_{i-1}\right\} 
\]
 (a configuration $\mathbf{p}$ is characterized by as much innovation
as more separated it is from the configurations of the previous era)\@.
\item Every region $R\in\mathcal{R}_{i}$ is given an innovation score defined
as:
\[
is\left(R\right)=\sum\left\{ \left.is\left(\mathbf{p}\right)\right|\mathbf{p}\in\mathscr{P}_{i}\cap R\right\} 
\]

\item The total innovation score for the entire era is:
\[
is_{TOT,i}=\sum_{R\in\mathcal{R}_{i}}is\left(R\right)
\]

\item The avarage innovation score for the entire era is also calculated
as:
\[
is_{av,i}=\frac{is_{TOT,i}}{\left|\mathcal{R}_{i}\right|}
\]
where $\left|\mathcal{R}_{i}\right|$ is the number of regions of
era $i$ .
\item $\mathcal{R}_{i}$ is partitioned in three subsets (their meaning
will be discussed later):

\begin{enumerate}
\item high innovation regions 
\[
\mathcal{R}_{i,h}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)>\alpha\cdot is_{av,i-1}\right\} 
\]
 where $\alpha$ is a constant defined by the designer (for example
$\alpha=1.2$). Each $R\in\mathcal{R}_{i,h}$ is split in $\mathcal{R}^{R}$
(as stated in def \ref{pers02.def:Splitting-a-region})
\item low innovation regions 
\[
\mathcal{R}_{i,l}=\left\{ \left.R\in\mathcal{R}_{i}\right|0<is\left(R\right)\le\alpha\cdot is_{av,i-1}\right\} 
\]
They are not changed.
\item no innovation regions 
\[
\mathcal{R}_{i,n}=\left\{ \left.R\in\mathcal{R}_{i}\right|is\left(R\right)=0\right\} 
\]

\end{enumerate}
\item Disjoint couples of contiguous regions $\left(R_{1},R_{2}\right)$,
with $R_{1},R_{2}\in\mathcal{R}_{i,n}$ are selected. The set of this
couples is indicated as $\mathcal{C}$. The couples of regions are
merged:
\[
\forall\left(R_{1},R_{2}\right)\in\mathcal{C}\Rightarrow R=R_{1}+R_{2}
\]
 (see def \ref{pers02.def:Merging-regions})
\item The set of regions $\mathcal{R}_{i+1}$ for the following era is defined
as:
\[
\mathcal{R}_{i+1}=
\]
\[
=\left(\bigcup_{R\in\mathcal{R}_{i,h}}\mathcal{R}^{R}\right)\cup\mathcal{R}_{i,l}\cup
\]
\[
\cup\left(\mathcal{R}_{i,n}\setminus\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left\{ R_{1},R_{2}\right\} \right)\cup
\]
\[
\cup\left(\bigcup_{\left(R_{1},R_{2}\right)\in\mathcal{C}}\left(R_{1}+R_{2}\right)\right)
\]

\end{enumerate}

\paragraph{TERMINATION CONDITION}
\begin{itemize}
\item The algorithm terminates at step $k$ if
\[
is_{TOT,k},is_{TOT,k-1},\dots,is_{TOT,k-\beta}\le\gamma\cdot is_{TOT,k-\left(\beta-1\right)}
\]
 where $\beta$ and $\gamma$ are selected by the experimenter (see
remark \ref{rem:termination}).\end{itemize}
\begin{rem}
\label{pers02.rem:smaller_regions}The rule \ref{pers02.enu:K} of
the iteration rules says that the smaller is a region, the more ``crowded''
it is. It means that configurations in smaller regions are evaluated
with more ``attention'' (see figure \ref{pers02.fig:small_and_big}).

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/small_and_big}

\caption{\label{pers02.fig:small_and_big}In this example 5 configurations
are evaluated in a small region and in a bigger region. In can be
seen that smaller region is more crowded.}

\end{figure}

\end{rem}

\begin{rem}
The rule \ref{pers02.enu:novelty_score_of_a_configuration} says that
a configuration whose objectives are more ``separated'' by the previous
Pareto front, has to be taken in greater account than others. A configuration
that is very near, in the objective space, to the previous Pareto
front doesn't add a true innovation. Therefore, the innovation score
of a configuration is a measure of how much interest we have in considering
it (see figure \ref{pers02.fig:Novelty-score-of-a-config}).

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/novelty_score}

\caption{\label{pers02.fig:Novelty-score-of-a-config}innovation score of a
configuration}

\end{figure}

\end{rem}

\begin{rem}
The innovation score of a region is a measure of how much different
are the points that it adds to Pareto Front compared to the previous
Pareto front. ``High innovation regions'' are the ones in which
more configurations are worth evaluating, because they add many points
on not yet well explored Pareto front areas. Therefore, these regions
are split in the next era (see remark \ref{pers02.rem:smaller_regions})
and more ``crowded'' by simulations. ``No innovation regions''
are the ones that have proved to add few points on Pareto fronts,
probably very near to previous Pareto front points and a Pareto front
point near to previous points is not so much interesting. Therefore
it's not worth evaluating many of their configurations and it is useful
to merge these regions , in order to less densely evaluate them.

ULTERIORI GIUSTIFICAZIONI SULL'IMPORTANZA DI CONSIDERARE LA DIVERSITA'
DELLE SOLUZIONI SI TROVA IN ext12.pag5 E ALTRI.
\end{rem}

\begin{rem}
\label{rem:termination}The algorithm terminates when in the last
$\beta$ iterations not a great ``amount of innovation'' has been
discovered. Therefore it is very probably that carrying on iterating
will not considerably change the Pareto front already formed. It's
not recommended to chose $\beta=1$, because it is possible that the
Pareto fronts $\mathbf{o}\left(\mathscr{P}_{k-1}\right)$ and $\mathbf{o}\left(\mathscr{P}_{k}\right)$
are not very different but next Pareto fronts could be. In other words,
it's unsafe to terminate as soon as the Pareto front doesn't change
enough, passing from an era to the next. It's better taking into account
more than one era.
\end{rem}
!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
FRONTS WERE NOT VERY DIFFERENT''? (CON ``WERE'' AL POSTO DI ``ARE'')

\begin{rem}
Merging and splitting the regions are very dynamic processes. A portion
of the parameter space can be populated by a large number of small
regions in some eras, but can be covered by a small number of large
regions in next eras. This can be explained saying that, after a number
of eras of intense exploration of a portion of parameter space, this
exploration has turned to be enough thorough and so it was time for
other portions to be minutely scanned.
\end{rem}

\section{Experiments}

\section{Conclusions}
This is the end

\balance

\bibliographystyle{IEEEtran} 
\bibliography{bibliography}

% TODO: G2012 bib not used ?

\end{document}

>>>>

\section{Introduction}

@@
